### 2018-01-19 manuscript.rmd
adjusted affiliations

Catriona Munro^1^\*, Stefan Siebert^1,2^\*, Felipe Zapata^1,3^, Mark Howison^4,5^, Alejandro Damian Serrano^1,10^, Samuel H. Church^1,6^, Freya Goetz^1,7^, Philip R. Pugh^8^, Steven H.D. Haddock^9^, Casey W. Dunn^1,10^**

@@

^3^ Current address: Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA

@@

^10^ Current address: Department of Ecology and Evolutionary Biology, Yale University, New Haven, CT 06520, USA

>>>>

Catriona Munro^1^\*, Stefan Siebert^1,2^\*, Felipe Zapata^3^, Mark Howison^4,5^, Alejandro Damian Serrano^1,10^, Samuel H. Church^1,6^, Freya E. Goetz^1,7^, Philip R. Pugh^8^, Steven H.D. Haddock^9^, Casey W. Dunn^10^**

@@

^3^ Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA

@@

^10^ Department of Ecology and Evolutionary Biology, Yale University, New Haven, CT 06520, USA
